Disconnected pseudo-$C_\ell$ covariances for projected datasets

### 2019-05-21 draft/paper.tex
added mask, fixed cls plot

Simulations were drawn from Gaussian fields that followed a fiducial power
spectrum. The fiducial cosmology (\red{For the 2-bin case}) is given by
$\Omega_{cdm} = 0.27$, $\Omega_b = 0.045$, $h = 0.67$, $A_s = 2.1 10^{-9}$ and
$n_s = 0.9$, where each term correspond, respectively, to the amount of cold
dark matter and baryons today, the reduced Hubble constant, the primordial
curvature fluctuation amplitude and the spectral index. The redshift bins are
shown in Fig.~\ref{fig:pz} and the theoretical $\cl$ are in
Fig.~\ref{fig:cl-2bins}. Since all parts of sky will not be equally observed, a
realist mask (see Fig.~\ref{fig:mask}) was applied.  The results shown here
were obtained using the same mas for each redshift bin, as it is expected to
be that way in real observations. We checked, however, that using different
masks yielded same results.

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{./figures/mask-lss1.png}
  \caption{Example of sky mask used in our analysis}
  \label{fig:mask}
\end{figure}

>>>>

Simulations were drawn from Gaussian fields that followed a fiducial power
spectrum. The fiducial cosmology (\red{For the 2-bin case}) is given by
$\Omega_{cdm} = 0.27$, $\Omega_b = 0.045$, $h = 0.67$, $A_s = 2.1 10^{-9}$ and
$n_s = 0.9$, where each term correspond, respectively, to the amount of cold
dark matter and baryons today, the reduced Hubble constant, the primordial
curvature fluctuation amplitude and the spectral index. The redshift bins are
shown in Fig.~\ref{fig:pz} and the theoretical $\cl$ are in
Fig.~\ref{fig:cl-2bins}. Since all parts of sky will not be equally observed,
realist masks (see Fig.~\ref{fig:mask}) were applied.  The results shown here
were obtained using the same mas for each redshift bin, as it is expected to
be that way in real observations. We checked, however, that using different
masks yielded same results.

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{./figures/mask-lss1.png}\\
  \includegraphics[width=\columnwidth]{./figures/mask-lss2.png}
  \caption{Sky mask used in our analysis}
  \label{fig:mask}
\end{figure}
